---
title: "Plots"
author: "Kevin Haase"
date: "5/23/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install and load packages
#install.packages("pacman")
library("pacman")

pacman::p_load(readr, dplyr, tidyr, reshape2,ggplot2, ggrepel, cowplot, ggforce, circlize, chisq.posthoc.test, trend, fitdistrplus)

```
```{r}
library(plotly)
library(htmlwidgets)
```


```{r}
setwd("C:/Users/haase_k/Desktop/SVNKevin/PhD-Anglerverhalten/modelling/Angler Model/NetLogo")
```




# Plots for bandit and EEI

import data
```{r}
bandit_1_results <- read_csv("model_04_1_bandit/model_output/1000runs/bandit_results.csv")
bandit_1_results$model <- "bandit_v1"

bandit_2_results <- read_csv("model_04_2_bandit/model_output/1000runs/bandit_04_2_results.csv")
bandit_2_results$model <- "bandit_v2"

EEI_1_results <- read_csv("model_04_1_EEI/model_output/1000runs/EEI_results.csv")
EEI_1_results$model <- "EEI_v1"

EEI_2_results <- read_csv("model_04_2_EEI/model_output/1000runs/EEI_04_2_results.csv")
EEI_2_results$model <- "EEI_v2"
```

combine data of the different models
```{r}
df <- rbind(bandit_1_results, bandit_2_results, EEI_1_results, EEI_2_results)

df_safe <- df
```















# Boat fishing

```{r}
df <- df_safe
df <- filter(.data = df, fishing_method == "Boot")
```


## Effect of parameter a

make one plot with the med, min, max of the different models over parameter a
```{r}
ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = median.per.day, col = model))+
  geom_hline(yintercept = 2.498526)+
  geom_line(aes(x = `value-of-parameter_a`, y = min.per.day, col = model), linetype = "dotted")+
  geom_hline(yintercept = 0.7571291, linetype = "dotted")+
  geom_line(aes(x = `value-of-parameter_a`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 8.003936, linetype = "dashed")

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = median.per.day, col = model))+
  geom_hline(yintercept = 2.498526)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = sd.per.day, col = model))+
  geom_hline(yintercept = 1.8713159)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = min.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 0.7571291)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 8.003936)
```



## Effect of parameter e

make one plot with the med, min, max of the different models over parameter e
```{r}
ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = median.per.day, col = model))+
  geom_hline(yintercept = 2.498526)+
  geom_line(aes(x = `value-of-parameter_e`, y = min.per.day, col = model), linetype = "dotted")+
  geom_hline(yintercept = 0.7571291, linetype = "dotted")+
  geom_line(aes(x = `value-of-parameter_e`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 8.003936, linetype = "dashed")

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = median.per.day, col = model))+
  geom_hline(yintercept = 2.498526)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = sd.per.day, col = model))+
  geom_hline(yintercept = 1.8713159)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = min.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 0.7571291)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 8.003936)
```



## Effect of both paramters


surf is a matrix to generate a flat surface at the value of the reality
split dived the data by the model (color would do the same for continuous variable)
in add_surface split = F remove multipüle surfaces for each model and showscale = F remove the color from the legend

```{r}
surf <- c(
  c(2.5, 2.5),
  c(2.5, 2.5)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~median.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on median ", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "median")))
 
fig


htmlwidgets::saveWidget(
                widget = fig, #the plotly object
                file = "figure.html", #the path & file name
                selfcontained = TRUE #creates a single html file
                )
```






```{r}
surf <- c(
  c(1.87, 1.87),
  c(1.87, 1.87)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~sd.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on SD", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "SD")))
 
fig
```



```{r}
surf <- c(
  c(0.76, 0.76),
  c(0.76, 0.76)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~min.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on min", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "min")))
 
fig
```



```{r}
surf <- c(
  c(8, 8),
  c(8, 8)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~max.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on max", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "max")))
 
fig
```




```{r}
surf <- c(
  c(0, 0),
  c(0, 0)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~mean.diff, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on difference in travel distance", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "difference to reality in travel distance")))
 
fig
```























# Charter fishing

```{r}
df <- df_safe
df <- filter(.data = df, fishing_method == "Kutter")
```


## Effect of parameter a

make one plot with the med, min, max of the different models over parameter a
```{r}
ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = median.per.day, col = model))+
  geom_hline(yintercept = 8.53)+
  geom_line(aes(x = `value-of-parameter_a`, y = min.per.day, col = model), linetype = "dotted")+
  geom_hline(yintercept = 2.37, linetype = "dotted")+
  geom_line(aes(x = `value-of-parameter_a`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 11.52, linetype = "dashed")

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = median.per.day, col = model))+
  geom_hline(yintercept = 8.53)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = sd.per.day, col = model))+
  geom_hline(yintercept = 2.73)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = min.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 2.37)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 11.52)
```



## Effect of parameter e

make one plot with the med, min, max of the different models over parameter e
```{r}
ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = median.per.day, col = model))+
  geom_hline(yintercept = 8.53)+
  geom_line(aes(x = `value-of-parameter_e`, y = min.per.day, col = model), linetype = "dotted")+
  geom_hline(yintercept = 2.37, linetype = "dotted")+
  geom_line(aes(x = `value-of-parameter_e`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 11.52, linetype = "dashed")

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = median.per.day, col = model))+
  geom_hline(yintercept = 8.53)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = sd.per.day, col = model))+
  geom_hline(yintercept = 2.73)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = min.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 2.37)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 11.52)
```



## Effect of both paramters


surf is a matrix to generate a flat surface at the value of the reality
split dived the data by the model (color would do the same for continuous variable)
in add_surface split = F remove multipüle surfaces for each model and showscale = F remove the color from the legend

```{r}
surf <- c(
  c(8.53, 8.53),
  c(8.53, 8.53)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~median.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on median ", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "median")))
 
fig
```






```{r}
surf <- c(
  c(2.73, 2.73),
  c(2.73, 2.73)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~sd.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on SD", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "SD")))
 
fig
```



```{r}
surf <- c(
  c(2.37, 2.37),
  c(2.37, 2.37)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~min.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on min", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "min")))
 
fig
```



```{r}
surf <- c(
  c(11.52, 11.52),
  c(11.52, 11.52)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~max.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on max", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "max")))
 
fig
```




```{r}
surf <- c(
  c(0, 0),
  c(0, 0)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~mean.diff, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on difference in travel distance", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "difference to reality in travel distance")))
 
fig
```


























# Land fishing

```{r}
df <- df_safe
df <- filter(.data = df, fishing_method == "Land")
```


## Effect of parameter a

make one plot with the med, min, max of the different models over parameter a
```{r}
ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = median.per.day, col = model))+
  geom_hline(yintercept = 1.59)+
  geom_line(aes(x = `value-of-parameter_a`, y = min.per.day, col = model), linetype = "dotted")+
  geom_hline(yintercept = 0.91, linetype = "dotted")+
  geom_line(aes(x = `value-of-parameter_a`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 4.54, linetype = "dashed")

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = median.per.day, col = model))+
  geom_hline(yintercept = 1.59)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = sd.per.day, col = model))+
  geom_hline(yintercept = 0.7)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = min.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 0.91)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_a`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 4.54)
```



## Effect of parameter e

make one plot with the med, min, max of the different models over parameter e
```{r}
ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = median.per.day, col = model))+
  geom_hline(yintercept = 1.59)+
  geom_line(aes(x = `value-of-parameter_e`, y = min.per.day, col = model), linetype = "dotted")+
  geom_hline(yintercept = 0.91, linetype = "dotted")+
  geom_line(aes(x = `value-of-parameter_e`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 4.54, linetype = "dashed")

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = median.per.day, col = model))+
  geom_hline(yintercept = 1.59)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = sd.per.day, col = model))+
  geom_hline(yintercept = 0.7)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = min.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 0.91)

ggplot(data = df)+
  geom_line(aes(x = `value-of-parameter_e`, y = max.per.day, col = model), linetype = "dashed")+
  geom_hline(yintercept = 4.54)
```



## Effect of both paramters


surf is a matrix to generate a flat surface at the value of the reality
split dived the data by the model (color would do the same for continuous variable)
in add_surface split = F remove multipüle surfaces for each model and showscale = F remove the color from the legend

```{r}
surf <- c(
  c(1.59, 1.59),
  c(1.59, 1.59)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~median.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on median ", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "median")))
 
fig
```






```{r}
surf <- c(
  c(0.7, 0.7),
  c(0.7, 0.7)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~sd.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on SD", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "SD")))
 
fig
```



```{r}
surf <- c(
  c(0.91, 0.91),
  c(0.91, 0.91)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~min.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on min", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "min")))
 
fig
```



```{r}
surf <- c(
  c(4.54, 4.54),
  c(4.54, 4.54)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~max.per.day, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on max", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "max")))
 
fig
```




```{r}
surf <- c(
  c(0, 0),
  c(0, 0)
)
dim(surf) <- c(2,2)
y <- c(0,1)
x <- c(0,1)
rownames(surf) <- x
colnames(surf) <- y

fig <- df %>% 
  plot_ly(x = ~`value-of-parameter_e`, y = ~`value-of-parameter_a`,z = ~mean.diff, split = ~model, type="scatter3d", mode = 'markers') %>%
  add_surface(z=~surf, x = ~x, y= ~y, opacity = 0.5, split = F, showscale=FALSE)%>%
  layout(title = " Parameter effect on difference in travel distance", scene = list(xaxis = list(title = "parameter e"), yaxis = list(title = "parameter a"), zaxis = list(title = "difference to reality in travel distance")))
 
fig
```










