---
title: "test_results_model04_EEI"
author: "Kevin Haase"
date: "3/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install and load packages
#install.packages("pacman")
library("pacman")

pacman::p_load(readr, dplyr, tidyr, reshape2,ggplot2, ggrepel, cowplot, ggforce, circlize, chisq.posthoc.test, trend)
```

```{r}
setwd("C:/Users/haase_k/Desktop/SVNKevin/PhD-Anglerverhalten/modelling/Angler Model/NetLogo/model_04_1_EEI_wrongOrder")
```












#Import data

The real world data is importet over the script "realworld_data".

## NetLogo

Netlogo model output of 210 runs (10 replication for each value of a) is importet below.

```{r}
EEI_angler <- read_csv("model_output/1000runs/angler.csv")
EEI_angler <- separate(data = EEI_angler, col = run_ID, into = c("run", "rep"), sep = "_", remove = F)

EEI_location <- read_csv("model_output/1000runs/location.csv")
EEI_location <- separate(data = EEI_location, col = run_ID, into = c("run", "rep"), sep = "_", remove = F)

EEI_parameter <- EEI_location %>%
  group_by(run, `value-of-parameter_a`, `value-of-parameter_e`) %>%
  summarise()
```









# gerneral model set up

## Number of angler (per fishing method)

```{r}
# total number per run
test <- EEI_angler %>%
  group_by(run_ID)%>%
  mutate(n.run = length(unique(who)))

# total number per fishing method
test <- test %>%
  group_by(run_ID, fishing_method, n.run)%>%
  summarise(n.method = length(unique(who)))

test <- mutate(.data = test, perc.angler = n.method/n.run)

test <- test %>%
  group_by(fishing_method) %>%
  summarise(mean(perc.angler),
            min(perc.angler),
            max(perc.angler))
```

correct distribution of fishing methods


## Origin of angler

```{r}
test <- EEI_angler %>%
  group_by(run_ID)%>%
  summarise(min_zip = min(homelocation_name),
            max_zip = max(homelocation_name))
```

correct range of zip codes








# Model comparison



## Fishing locations visited

anzahl fishing locations

```{r}

test <- filter(.data = EEI_location, visited == TRUE)
test <- test %>%
  group_by(run_ID, location_method) %>%
  summarise(n.locations = length(unique(location_name)))

range(test$n.locations[test$location_method == "Boot"])
range(test$n.locations[test$location_method == "Kutter"])
range(test$n.locations[test$location_method == "Land"])
```

```{r}
test <- filter(.data = EEI_location, visited == TRUE)
test <- test %>%
  group_by(run, location_method) %>%
  summarise(n.locations = length(unique(location_name)))

EEI_parameter <- left_join(EEI_parameter, test)
```








## Distribution between fishing locations (key metric)


```{r}
#for each experiment
test <- EEI_location %>%
  group_by(run_ID, location_method)%>%
  mutate(n.total.fishingday.exp = sum(total_visits))

test <- mutate(.data = test, perc_exp = (total_visits/n.total.fishingday.exp)*100)

test <- test%>%
  group_by(run_ID, run, rep, location_method)%>%
  summarise(mean.perc_exp = mean(perc_exp),
            median.perc_exp = median(perc_exp),
            sd.perc_exp = sd(perc_exp),
            min.perc_exp = min(perc_exp),
            max.perc_exp = max(perc_exp))


test <- test %>%
  group_by(run, location_method) %>%
  summarise(mean.perc_allrep = mean(mean.perc_exp),
            median.perc_allrep = mean(median.perc_exp),
            sd.perc_allrep = mean(sd.perc_exp),
            min.perc_allrep = mean(min.perc_exp),
            max.perc_allrep = mean(max.perc_exp))

```




## angler per day


```{r}
EEI_location <- mutate(.data = EEI_location, ang.per.day = total_visits/365)


test <- EEI_location %>%
  group_by(run, run_ID, location_method)%>%
  mutate(sum.ang.per.day = sum(ang.per.day))

test <- mutate(.data = test, perc.per.day = (ang.per.day/sum.ang.per.day)*100)



test <- test %>%
  group_by(run, run_ID, location_method) %>%
  summarise(mean.per.day = mean(perc.per.day),
            median.per.day = median(perc.per.day),
            sd.per.day = sd(perc.per.day),
            min.per.day = min(perc.per.day),
            max.per.day = max(perc.per.day))

test <- test %>%
  group_by(run, location_method) %>%
  summarise(mean.per.day = mean(mean.per.day),
            median.per.day = mean(median.per.day),
            sd.per.day = mean(sd.per.day),
            min.per.day = mean(min.per.day),
            max.per.day = mean(max.per.day))
```



```{r}
EEI_parameter <- left_join(EEI_parameter, test)
```









## Average differences in travel distances

Three data frames are needed: run is the netlogo model output, dat the real world angler data, and dist the distance between fishing location and zip_codes

```{r}
run <- EEI_angler
dat <- dat_zip
dat <- filter(.data = dat, zip_code > 9999 & zip_code < 33000 | 
                            zip_code > 37999 & zip_code < 40000 |
                            zip_code > 48999 & zip_code < 50000)
dist <- dist_safe



#transform 5 digit zipcode to 2 digit
run$zip_code <- formatC(run$homelocation_name, width = 5, format = "d", flag = "0")
run$zip_code <- as.numeric(substr(run$zip_code, 1, 2))

dat$zip_code <- formatC(dat$zip_code, width = 5, format = "d", flag = "0")
dat$zip_code <- as.numeric(substr(dat$zip_code, 1, 2))

dist$zip_code <- formatC(dist$zip_code, width = 5, format = "d", flag = "0")
dist$zip_code <- as.numeric(substr(dist$zip_code, 1, 2))
dist <- dist %>%
  group_by(zip_code, ap_code) %>%
  summarise(distance = mean(distance_km))



#rename colums to match each other 
names(dat)[names(dat) == "harbour_code"] <- "ap_code"
```



combine both datasets with distances
```{r}
dat <- left_join(dat, dist)
names(dat)[names(dat) == "survey_category"] <- "fishing_method"
```

calculate travel distances per zip code
```{r}
run <- mutate(.data = run, mean.dist.ang = total_traveled_dist/total_angler_trips)
run <- filter( .data = run, total_angler_trips > 0)

run <- run %>%
  group_by(run, fishing_method, zip_code) %>%
  summarise(mean.dist.e = mean(mean.dist.ang),
            med.dist.e = median(mean.dist.ang),
            SD.dist.e = sd(mean.dist.ang),
            min.dist.e = min(mean.dist.ang),
            max.dist.e = max(mean.dist.ang))

dat <- filter( .data = dat, distance > 0)
dat <- dat %>%
  group_by(fishing_method, zip_code) %>%
  summarise(mean.dist = mean(distance),
            med.dist = median(distance),
            SD.dist = sd(distance),
            min.dist = min(distance),
            max.dist = max(distance))

```


```{r}
test <- left_join(run, dat)

test <- mutate(.data = test, mean.diff = mean.dist - mean.dist.e,
                              med.diff = med.dist - med.dist.e,
                              SD.diff = SD.dist - SD.dist.e,
                              min.diff = min.dist - min.dist.e,
                              max.diff = max.dist - max.dist.e)


test2 <- test %>%
  group_by(run, fishing_method)%>%
  summarise(mean.diff = mean(abs(mean.diff)),
            med.diff = mean(abs(med.diff)),
            SD.diff = mean(abs(SD.diff)),
            min.diff = mean(abs(min.diff)),
            max.diff = mean(abs(max.diff)))
```


```{r}
names(EEI_parameter)[names(EEI_parameter) == "location_method"] <- "fishing_method"
EEI_parameter <- left_join(EEI_parameter, test2)

write.table(EEI_parameter, "model_output/1000runs/EEI_wrongOrder_results.csv", sep = ",", row.names = FALSE)
```


percentage difference of travel distance
```{r}
test <- mutate(.data = test, perc.mean.dist = (mean.dist.e/mean.dist)*100,
                              perc.med.dist = (med.dist.e/med.dist)*100,
                              perc.SD.dist = (SD.dist.e/SD.dist)*100,
                              perc.min.dist = (min.dist.e/min.dist)*100,
                              perc.max.dist = (max.dist.e/max.dist)*100)

test <- mutate(.data = test, perc.diff.mean.dist = abs(100 - perc.mean.dist),
                              perc.diff.med.dist = abs(100 - perc.med.dist),
                              perc.diff.SD.dist = abs(100 - perc.SD.dist),
                              perc.diff.min.dist = abs(100 - perc.min.dist),
                              perc.diff.max.dist = abs(100 - perc.max.dist))

perc.diff.travel <- test %>%
  group_by(run, fishing_method)%>%
  summarise(mean.perc.diff.mean.dist = mean(perc.diff.mean.dist),
            mean.perc.diff.med.dist = mean(perc.diff.med.dist),
            mean.perc.diff.SD.dist = mean(perc.diff.SD.dist),
            mean.perc.diff.min.dist = mean(perc.diff.min.dist),
            mean.perc.diff.max.dist = mean(perc.diff.max.dist))
```






# comparison to reality

##unweighted difference of each calibration metric to the reality

```{r}
test <- left_join(EEI_parameter, real_values)

test <- mutate(.data = test, dif.n.location = real.n.locations - n.locations,
                              dif.mean = real.mean.ang.per.sample - mean.per.day,
                              dif.med = real.median.ang.per.sample - median.per.day,
                              dif.sd = real.sd.ang.per.sample - sd.per.day,
                              dif.min = real.min.ang.per.sample - min.per.day,
                              dif.max = real.max.ang.per.sample - max.per.day)

test <- subset(x = test, select = c(run, `value-of-parameter_a`, `value-of-parameter_e`, fishing_method, dif.n.location, dif.mean, dif.med, dif.sd, dif.min, dif.max, mean.diff))
```



##weighted difference of each calibration metric to the reality

idea: as the metric vary in their values (percent in key metric, number of locations, and kilometer traveled), we need to standardize and do it with percentages of the model output to the real value.
How to do it:
- for each metric is the real value = 100%
- the model output value is X% of the real value
- calculate the difference from output to real and sum over all metric
- smallest sum is the best parameter combination


### for # harbours and key metric

real values are stored in dataframe "real_values"
model output in the dataframes "theoryXY_paramter"
```{r}
test <- left_join(EEI_parameter, real_values)
test <- subset(x = test, select = -c(mean.diff))
```


calculate percentage of model output to reality
than the difference to 100%
than sum up the percentage per parameter combination
```{r}
test <- mutate(.data = test, perc.n.locations = (n.locations/real.n.locations)*100,
                              perc.mean = (mean.per.day/real.mean.ang.per.sample)*100,
                              perc.med = (median.per.day/real.median.ang.per.sample)*100,
                              perc.sd = (sd.per.day/real.sd.ang.per.sample)*100,
                              perc.min = (min.per.day/real.min.ang.per.sample)*100,
                              perc.max = (max.per.day/real.max.ang.per.sample)*100)

test <- mutate(.data = test, perc.diff.n.locations = abs(100 - perc.n.locations),
                              perc.diff.mean = abs(100 - perc.mean),
                              perc.diff.med = abs(100 - perc.med),
                              perc.diff.sd = abs(100 - perc.sd),
                              perc.diff.min = abs(100 - perc.min),
                              perc.diff.max = abs(100 - perc.max))

test <- mutate(.data = test, sum.perc.diff = perc.diff.n.locations + perc.diff.mean + perc.diff.med + perc.diff.sd + perc.diff.min + perc.diff.max)

perc.diff <- test %>%
  group_by(run, `value-of-parameter_a`, `value-of-parameter_e`, fishing_method, perc.diff.n.locations, perc.diff.mean, perc.diff.med, perc.diff.sd, perc.diff.min, perc.diff.max, sum.perc.diff) %>%
  summarise()
```


put together percentage difference of number locations and key metric with travel percentage difference
```{r}
perc.diff <- left_join(perc.diff, perc.diff.travel)

perc.diff <- mutate(.data = perc.diff, sum.perc.diff = sum.perc.diff + mean.perc.diff.mean.dist)
perc.diff <- mutate(.data = perc.diff, new.sum.perc.diff = sum.perc.diff + mean.perc.diff.med.dist + mean.perc.diff.SD.dist + mean.perc.diff.min.dist + mean.perc.diff.max.dist)



perc.diff <- subset(x = perc.diff, select = c(run, `value-of-parameter_a`, `value-of-parameter_e`, fishing_method, perc.diff.n.locations, perc.diff.mean, perc.diff.med, perc.diff.sd, perc.diff.min, perc.diff.max, mean.perc.diff.mean.dist, sum.perc.diff, mean.perc.diff.med.dist ,mean.perc.diff.SD.dist ,mean.perc.diff.min.dist ,mean.perc.diff.max.dist, new.sum.perc.diff))
```



```{r}
write.table(perc.diff, "model_output/1000runs/EEI_wrongOrder_perc_diff.csv", sep = ",", row.names = FALSE)
```


