---
title: "test_results_model04"
author: "Kevin Haase"
date: "3/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install and load packages
#install.packages("pacman")
library("pacman")

pacman::p_load(readr, dplyr, tidyr, reshape2,ggplot2, ggrepel, cowplot, ggforce, circlize, chisq.posthoc.test, trend)
```

```{r}
setwd("C:/Users/haase_k/Desktop/SVNKevin/PhD-Anglerverhalten/modelling/Angler Model/NetLogo/model_04_1_utility")
```














#Import data

The real world data is importet over the script "realworld_data".

## NetLogo

Netlogo model output of 210 runs (10 replication for each value of a) is importet below.

```{r}
#Loop um viele Datensätze einzuladen
#erzeuge eine Liste (save_files) mit 23 Plätzen wo die files reingespeichert werden
save_files <- list()
save_files <- vector(mode = "list", length = 207)
#Objekt erzeugen wo die Namen drin stehen wie sie gespeichert herißen
names <- paste("model_output/run_", 1:207, ".csv", sep = "")
names
#Alternative
#test <- list.files(file.path("C:/Users/haase_k/Desktop/SVNKevin/PhD-Anglerverhalten/modelling/Angler Model/NetLogo/model_03/model_output"))

#Schleife um die Datensätze einzulesen
for (i in 1:207) {
  save_files[[i]] <- read_csv(file = names[i], 
                              col_names = c("model_run", "parameter_a", "time", "ID", "homelocation", "fishing_method", "location", "location_method", "catch"), show_col_types = FALSE)
  #print(i)
}
#wendet eine Funktion "rbind" auf eine liste an
netlogo_utility <- do.call(rbind, save_files)
netlogo_utility$model_run <- as.character(netlogo_utility$model_run)

netlogo_utility_safe <- netlogo_utility
```



## ML3

ML3 model output of 210 runs (10 replication for each value of a) is importet below.

```{r}
#Loop um viele Datensätze einzuladen
#erzeuge eine Liste (save_files) mit 23 Plätzen wo die files reingespeichert werden
save_files <- list()
save_files <- vector(mode = "list", length = 210)
#Objekt erzeugen wo die Namen drin stehen wie sie gespeichert herißen

names <- paste("results-M_U-10exp/run-",0:209,".csv", sep = "")
names
#Alternative
#test <- list.files(file.path("C:/Users/haase_k/Desktop/SVNKevin/PhD-Anglerverhalten/modelling/Angler Model/NetLogo/model_03/model_output"))

#Schleife um die Datensätze einzulesen
for (i in 1:210) {
  save_files[[i]] <- read_csv(file = names[i], 
                              show_col_types = FALSE, 
                              col_types = cols(Angler_postcode = col_double(), ID = col_double(), time = col_double())
                              )
  #print(i)
}


model_run <- paste("run-", 0:209, sep = "")
save_files <- mapply(cbind, save_files, "model_run"=model_run, SIMPLIFY=F)

parameter_a <- rep(seq(0,1,0.05), each = 10)
save_files <- mapply(cbind, save_files, "parameter_a"=parameter_a, SIMPLIFY=F)
#wendet eine Funktion "rbind" auf eine liste an
ml3_utility <- do.call(rbind, save_files)

names(ml3_utility)[names(ml3_utility) == "Angler_fishing_method"] <- "fishing_method"
names(ml3_utility)[names(ml3_utility) == "Angler_postcode"] <- "homelocation"
names(ml3_utility)[names(ml3_utility) == "FishingLocation"] <- "location"
names(ml3_utility)[names(ml3_utility) == "FishingLocation_method"] <- "location_method"

ml3_utility_safe <- ml3_utility
```





```{r}
netlogo_utility$model <- "NetLogo"
ml3_utility$model <- "ML3"

utility <- bind_rows(netlogo_utility, ml3_utility)

utility_safe <- utility
```



```{r}
utility_parameter <- utility %>%
  group_by(model, parameter_a) %>%
  summarise()
```












# gerneral model set up

## Number of angler (per survey category)

```{r}

test <- utility %>%
  group_by(model, model_run, parameter_a)%>%
  mutate(n.run = length(unique(ID)))

test <- test %>%
  group_by(model, model_run, parameter_a, fishing_method, n.run)%>%
  summarise(n.method = length(unique(ID)))

test <- mutate(.data = test, perc.angler = n.method/n.run)

test <- test %>%
  group_by(model, parameter_a, fishing_method) %>%
  summarise(mean(perc.angler))
```

correct distribution of fishing methods


## Origin of angler

```{r}
test <- utility %>%
  group_by(model, model_run, parameter_a)%>%
  summarise(min_zip = min(homelocation),
            max_zip = max(homelocation))
```

correct range of zip codes


## Fishing method

Are all angler driving to locations with the same fishing method?
```{r}
netlogo_utility$location[netlogo_utility$location_method != netlogo_utility$fishing_method]
ml3_utility$location[ml3_utility$location_method != ml3_utility$fishing_method]
```






# Model comparison



## Fishing locations visited

anzahl fishing locations

```{r}
test <- utility %>%
  group_by(model, model_run, parameter_a, fishing_method) %>%
  summarise(n.locations = length(unique(location)))

range(test$n.locations[test$fishing_method == "Boot"])
range(test$n.locations[test$fishing_method == "Kutter"])
range(test$n.locations[test$fishing_method == "Land"])
```

with a = 1 only 30 of 33 boat locations are visited

```{r}
test <- utility %>%
  group_by(model, parameter_a, fishing_method) %>%
  summarise(n.locations = length(unique(location)))

utility_parameter <- left_join(utility_parameter, test)
```








## Distribution between fishing locations (key metric)


```{r}
#for each experiment
test <- utility %>%
  group_by(model, model_run, parameter_a, fishing_method)%>%
  mutate(n.total.fishingday.exp = length(ID))

test <- test %>%
  group_by(model, model_run, parameter_a, fishing_method, n.total.fishingday.exp, location)%>%
  summarise(n.fishingday.exp = length(ID))

test <- mutate(.data = test, perc_exp = n.fishingday.exp/n.total.fishingday.exp)

test <- test%>%
  group_by(model, model_run, parameter_a, fishing_method)%>%
  summarise(mean.perc_exp = mean(perc_exp)*100,
            median.perc_exp = median(perc_exp)*100,
            sd.perc_exp = sd(perc_exp)*100,
            min.perc_exp = min(perc_exp)*100,
            max.perc_exp = max(perc_exp)*100)


test <- test %>%
  group_by(model, parameter_a, fishing_method) %>%
  summarise(mean.perc_allruns = mean(mean.perc_exp),
            median.perc_allruns = mean(median.perc_exp),
            sd.perc_allruns = mean(sd.perc_exp),
            min.perc_allruns = mean(min.perc_exp),
            max.perc_allruns = mean(max.perc_exp))

```


## angler per day

```{r}
run <- utility_safe

run$trip_count <- 1

run <- run %>%
  group_by(model, parameter_a, model_run, location, location_method) %>%
  summarise(total_visits = sum(trip_count))


run <- mutate(.data = run, ang.per.day = total_visits/365)


test <- run %>%
  group_by(model, parameter_a, model_run, location_method)%>%
  mutate(sum.ang.per.day = sum(ang.per.day))

test <- mutate(.data = test, perc.per.day = (ang.per.day/sum.ang.per.day)*100)



test <- test %>%
  group_by(model, parameter_a, model_run, location_method) %>%
  summarise(mean.per.day = mean(perc.per.day),
            median.per.day = median(perc.per.day),
            sd.per.day = sd(perc.per.day),
            min.per.day = min(perc.per.day),
            max.per.day = max(perc.per.day))

test <- test %>%
  group_by(model, parameter_a, location_method) %>%
  summarise(mean.per.day = mean(mean.per.day),
            median.per.day = mean(median.per.day),
            sd.per.day = mean(sd.per.day),
            min.per.day = mean(min.per.day),
            max.per.day = mean(max.per.day))
```

```{r}
names(test)[names(test) == "location_method"] <- "fishing_method"

utility_parameter <- left_join(utility_parameter, test)
```











## Average percentage distribution of the angler distribution

netlogo and real world data is needed for this comparison

```{r}
run <- utility_safe
dat <- dat_zip
dat <- filter(.data = dat, zip_code > 9999 & zip_code < 33000 | 
                            zip_code > 37999 & zip_code < 40000 |
                            zip_code > 48999 & zip_code < 50000)
```


```{r}
#Netlogo
run <- run %>%
  group_by(model, model_run, parameter_a)%>%
  mutate(n.total.fishingday.exp = length(ID))

run <- run %>%
  group_by(model,model_run, parameter_a, n.total.fishingday.exp, location)%>%
  summarise(n.fishingday.exp = length(ID))

run <- mutate(.data = run, perc_exp = n.fishingday.exp/n.total.fishingday.exp)

run <- run %>%
  group_by(model,parameter_a, location) %>%
  summarise(n.total.fishingday.exp = mean(n.total.fishingday.exp),
            n.fishingday.exp = mean(n.fishingday.exp),
            perc_exp = mean(perc_exp))


#in the real World
dat <- mutate(.data = dat, n.total.fishingday = length(ID))

dat <- dat %>%
  group_by(n.total.fishingday, harbour_code) %>%
  summarise(n.fishingday = length(ID))

dat <- mutate(.data = dat, perc_data = n.fishingday/n.total.fishingday)



names(run)[names(run) == "location"] <- "harbour_code"
test <- left_join(dat, run)


test$diff <- test$perc_data - test$perc_exp
test %>%
  group_by(model, parameter_a) %>%
  summarise(mean.diff = mean(abs(diff), na.rm = T))


test <- mutate(.data = test, perc.diff = ((perc_exp*100)/perc_data)-100)
test %>%
  group_by(model, parameter_a) %>%
  summarise(mean.diff = mean(abs(perc.diff), na.rm = T))
```














## Average differences in travel distances

Three data frames are needed: run is the netlogo model output, dat the real world angler data, and dist the distance between fishing location and zip_codes

```{r}
run <- utility_safe
dat <- dat_zip
dat <- filter(.data = dat, zip_code > 9999 & zip_code < 33000 | 
                            zip_code > 37999 & zip_code < 40000 |
                            zip_code > 48999 & zip_code < 50000)
dist <- dist_safe



#transform 5 digit zipcode to 2 digit
run$zip_code <- formatC(run$homelocation, width = 5, format = "d", flag = "0")
run$zip_code <- as.numeric(substr(run$zip_code, 1, 2))

dat$zip_code <- formatC(dat$zip_code, width = 5, format = "d", flag = "0")
dat$zip_code <- as.numeric(substr(dat$zip_code, 1, 2))

dist$zip_code <- formatC(dist$zip_code, width = 5, format = "d", flag = "0")
dist$zip_code <- as.numeric(substr(dist$zip_code, 1, 2))
dist <- dist %>%
  group_by(zip_code, ap_code) %>%
  summarise(distance = mean(distance_km))



#rename colums to match each other 
names(run)[names(run) == "location"] <- "ap_code"
names(dat)[names(dat) == "harbour_code"] <- "ap_code"
```



combine both datasets with distances
```{r}
run <- left_join(run, dist)

dat <- left_join(dat, dist)
names(dat)[names(dat) == "survey_category"] <- "fishing_method"
```

calculate travel distances per zip code
```{r}
run <- run %>%
  group_by(model, parameter_a, fishing_method, zip_code) %>%
  summarise(min.dist.e = min(distance),
            max.dist.e = max(distance),
            mean.dist.e = mean(distance))
run <- mutate(.data = run, diff.e = max.dist.e - min.dist.e)

dat <- dat %>%
  group_by(fishing_method, zip_code) %>%
  summarise(min.dist = min(distance),
            max.dist = max(distance),
            mean.dist = mean(distance))
dat <- mutate(.data = dat, diff = max.dist - min.dist)
```


```{r}
test <- left_join(run, dat)

test <- test %>%
  group_by(model, parameter_a, fishing_method, zip_code)%>%
  mutate(min.diff = min.dist - min.dist.e,
          max.diff = max.dist - max.dist.e,
          mean.diff = mean.dist - mean.dist.e,
          diff.diff = diff - diff.e)

test2 <- test %>%
  group_by(model, parameter_a, fishing_method)%>%
  summarise(mean = mean(abs(mean.diff)))
```


```{r}
utility_parameter <- left_join(utility_parameter, test2)

write.table(utility_parameter, "model_output/utility_results.csv", sep = ",", row.names = FALSE)
```


percentage difference of travel distance
```{r}
test <- mutate(.data = test, perc.dist = (mean.dist.e/mean.dist)*100)

test <- mutate(.data = test, perc.diff.dist = abs(100 - perc.dist))

perc.diff.travel <- test %>%
  group_by(model, parameter_a, fishing_method)%>%
  summarise(mean.perc.diff.dist = mean(perc.diff.dist))
```





plots to show difference in travel distance


```{r}
dat_test <- filter(.data = dat, fishing_method == "Boot")
run_test <- filter(.data = run, fishing_method == "Boot")

ggplot()+
  geom_pointrange(data = dat_test, aes(x = mean.dist, y = zip_code, xmin = min.dist, xmax = max.dist))+
  geom_pointrange(data = run_test, aes(x = mean.dist.e, y = zip_code+0.5, xmin = min.dist.e, xmax = max.dist.e), col = "red")
```


```{r}
dat_test <- filter(.data = dat, fishing_method == "Kutter")
run_test <- filter(.data = run, fishing_method == "Kutter")

ggplot()+
  geom_pointrange(data = dat_test, aes(x = mean.dist, y = zip_code, xmin = min.dist, xmax = max.dist))+
  geom_pointrange(data = run_test, aes(x = mean.dist.e, y = zip_code+0.5, xmin = min.dist.e, xmax = max.dist.e), col = "red")
```


```{r}
dat_test <- filter(.data = dat, fishing_method == "Land")
run_test <- filter(.data = run, fishing_method == "Land")

ggplot()+
  geom_pointrange(data = dat_test, aes(x = mean.dist, y = zip_code, xmin = min.dist, xmax = max.dist))+
  geom_pointrange(data = run_test, aes(x = mean.dist.e, y = zip_code+0.5, xmin = min.dist.e, xmax = max.dist.e), col = "red")
```












# comparison to reality

##unweighted difference of each calibration metric to the reality
```{r}
test <- left_join(utility_parameter, real_values)

test <- mutate(.data = test, dif.n.location = real.n.locations - n.locations,
                              dif.mean = real.mean.ang.per.sample - mean.per.day,
                              dif.med = real.median.ang.per.sample - median.per.day,
                              dif.sd = real.sd.ang.per.sample - sd.per.day,
                              dif.min = real.min.ang.per.sample - min.per.day,
                              dif.max = real.max.ang.per.sample - max.per.day)

test <- subset(x = test, select = c(model, parameter_a, fishing_method, dif.n.location, dif.mean, dif.med, dif.sd, dif.min, dif.max, mean))
```

##weighted difference of each calibration metric to the reality

idea: as the metric vary in their values (percent in key metric, number of locations, and kilometer traveled), we need to standardize and do it with percentages of the model output to the real value.
How to do it:
- for each metric is the real value = 100%
- the model output value is X% of the real value
- calculate the difference from output to real and sum over all metric
- smallest sum is the best parameter combination


### for # harbours and key metric

real values are stored in dataframe "real_values"
model output in the dataframes "theoryXY_paramter"
```{r}
test <- left_join(utility_parameter, real_values)
test <- subset(x = test, select = -c(mean))
```


calculate percentage of model output to reality
than the difference to 100%
than sum up the percentage per parameter combination
```{r}
test <- mutate(.data = test, perc.n.locations = (n.locations/real.n.locations)*100,
                              perc.mean = (mean.per.day/real.mean.ang.per.sample)*100,
                              perc.med = (median.per.day/real.median.ang.per.sample)*100,
                              perc.sd = (sd.per.day/real.sd.ang.per.sample)*100,
                              perc.min = (min.per.day/real.min.ang.per.sample)*100,
                              perc.max = (max.per.day/real.max.ang.per.sample)*100)

test <- mutate(.data = test, perc.diff.n.locations = abs(100 - perc.n.locations),
                              perc.diff.mean = abs(100 - perc.mean),
                              perc.diff.med = abs(100 - perc.med),
                              perc.diff.sd = abs(100 - perc.sd),
                              perc.diff.min = abs(100 - perc.min),
                              perc.diff.max = abs(100 - perc.max))

test <- mutate(.data = test, sum.perc.diff = perc.diff.n.locations + perc.diff.mean + perc.diff.med + perc.diff.sd + perc.diff.min + perc.diff.max)

perc.diff <- test %>%
  group_by(model, parameter_a, fishing_method, perc.diff.n.locations, perc.diff.mean, perc.diff.med, perc.diff.sd, perc.diff.min, perc.diff.max, sum.perc.diff) %>%
  summarise()
```


put together percentage difference of number locations and key metric with travel percentage difference
```{r}
perc.diff <- left_join(perc.diff, perc.diff.travel)

perc.diff <- mutate(.data = perc.diff, sum.perc.diff = sum.perc.diff + mean.perc.diff.dist)

perc.diff <- subset(x = perc.diff, select = c(model, parameter_a, fishing_method, perc.diff.n.locations, perc.diff.mean, perc.diff.med, perc.diff.sd, perc.diff.min, perc.diff.max, mean.perc.diff.dist, sum.perc.diff))
```





```{r}
write.table(perc.diff, "model_output/utility_perc_diff.csv", sep = ",", row.names = FALSE)
```



















